%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PlushCV - One Page Two Column Resume
% LaTeX Template
% Version 1.0 (11/28/2021)
%
% Author:
% Shubham Mazumder (http://mazumder.me)
%
% Hacked together from:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Figure out a smoother way for the document to flow onto the next page.
% 3. Add more icon options 
% 4. Fix hacky left alignment on contact line
% 5. Remove Hacky fix for awkward extra vertical space
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the vertical limit.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%Icons:
%%Main: https://icons8.com/icons/carbon-copy
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{plushcv}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Ryan}{Blanchette}{Data Professional }{\contactline{\href{https://www.github.com/jblanche1325}{jblanche1325}}{\href{https://www.linkedin.com/in/ryanblanchette13}{ryanblanchette13}}{\href{mailto:jblanche1325@gmail.com}{jblanche1325@gmail.com}}{\href{tel:+19016065143}{(901)606-5143}}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.70\textwidth} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE PART 1
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{AutoZone}
\descript{| Sr. HR Business Intelligence Analyst }
\location{June 2022 – Present | Memphis, Tennessee}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\sectionsep
\item Performed complex joins and aggregations with HR data in BigQuery to produce highly detailed adhoc people analytics for various parts of the business including supply chain, compensation, and DEI.
\item Collaborated with data engineering and architecture to design employee history tables that allowed the HRIS team to give valuable insights to HR at a much faster pace than legacy systems would allow.
\item Developed dashboards using BigQuery and Looker to replace legacy reports that provided superior insights at a greater speed.
\item Performed statistical testing on a supply chain initiative by collecting the necessary data and applying Fisher's test to show that the test locations had a significant improvement in new hire retention.
\item Replaced an existing 3rd party pay equity regression model using scikit-learn and other Python libraries with an $R^2$ over 90\% that helped ensure that employees were being paid fairly regardless of gender of ethnicity.
\end{tightemize}
\sectionsep

\runsubsection{Asurion}
\descript{| Sr. Business Intelligence Developer }
\location{August 2021 – June 2022 | Nashville, Tennessee}

\begin{tightemize}
\sectionsep
\item Deployed new tables and stored procedures into production, enhancing the supply chain data model.
\item Facilitated the transition from on-premises to cloud-based storage for supply chain data entities.
\item Addressed finance/supply chain needs by creating and updating tables, stored procedures, and reports.
\end{tightemize}
\sectionsep

\runsubsection{University of Tennessee}
\descript{| Data Analyst }
\location{September 2019 – August 2021 | Knoxville, Tennessee}
\begin{tightemize}
\sectionsep
\item Collected and cleaned data for critical engineering college surveys, contributing to ongoing success.
\item Transitioned from manual processes to Microsoft SQL Server, R, and Power BI for data processing and reporting.
\item Designed Power BI dashboards for engineering college leadership, providing visual insights.
\end{tightemize}
\sectionsep

\runsubsection{Jewelry Television}
\descript{| Data Analyst }
\location{August 2018 – September 2019 | Knoxville, Tennessee}
\begin{tightemize}
\sectionsep
\item Led the Analytics team in adopting big data technologies like Hive and Spark, improving efficiency.
\item Maintained reports on marketing campaign effectiveness using R, guiding future campaigns.
\item Engaged executive-level management to discuss data-driven goals and analytics opportunities.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.25\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming/Tools}
\sectionsep
\location{Proficient:}
Python \textbullet{} SQL \textbullet{} R  \\
Excel \textbullet{} BigQuery \\
\sectionsep
\location{Experienced:}
Tableau \textbullet{} Power Platform \textbullet{}  \\
Linux \textbullet{} GCP \\
\sectionsep
\location{Familiar:}
AWS \textbullet{} HTML \textbullet{} Vertex AI \\
\sectionsep
\sectionsep
\subsection{Libraries/Frameworks}
\sectionsep
Sklearn \textbullet{} PyCaret \textbullet{} \\
Pandas \textbullet{} BeautifulSoup \textbullet{} \\
Tidyverse \textbullet{} Shiny \\
Plotly \textbullet{} Keras \\
Spark


\sectionsep
\sectionsep
\subsection{Technical}
\sectionsep
Machine Learning \textbullet{} Statistics \\
Time Series Forecasting \textbullet{} \\
NLP  \textbullet{} Data Visualization \textbullet{} ETL \\
Hypothesis Testing \textbullet{} \\ 
Cloud Computing \textbullet{} MLOps \\
Data Engineering \\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{University of 
\\Tennessee}
\descript{Master's in Business Analytics}
\location{December 2016 | Knoxville, Tennessee}
Haslam College of Business \\
\location{ GPA: 3.80 / 4.00 }

\sectionsep
\subsection{University of
\\Tennessee}
\descript{Bachelor's in Statistics}
\location{May 2015 | Knoxville, Tennessee}
College of Arts and Sciences \\
\location{ GPA: 3.75 / 4.00 }
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CERTIFICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certifications} 
\subsection{Amazon Web Services}
\descript{Cloud Practitioner}
\location{December 2021}


\end{minipage} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     PAGE TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage

\begin{minipage}[t]{1.0\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE PART 2
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience (cont.)}

\runsubsection{UnitedHealth Group}
\descript{| Healthcare Economics Consultant }
\location{December 2016 – August 2018 | Remote}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\sectionsep
\item Developed SAS analytics to identify fraudulent medical claims, resulting in substantial savings.
\item Contributed to the development of a healthcare provider exploration tool using Tableau.
\item Explored vendor claims data using machine learning in R and SAS Enterprise Miner.
\end{tightemize}
\sectionsep

\runsubsection{University of Tennessee}
\descript{| Graduate Teaching Assistant }
\location{August 2015 – May 2016 | Knoxville, Tennessee}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\sectionsep
\item Guided senior undergraduate students in statistics through emails, office hours, and study sessions.
\item Experimented with different statistical packages to modernize courses.
\end{tightemize}
\sectionsep

\runsubsection{University of Tennessee}
\descript{| Mathematics Tutor }
\location{January 2014 – May 2015 | Knoxville, Tennessee}
\begin{tightemize}
\sectionsep
\item Coached mathematics students, improving understanding through examples and homework help.
\item Collaborated with supervisor to enhance the tutorial center, resulting in an improved tutor schedule.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Publications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications}

Blanchette, R., A. Khojandi, D. Cox, M. Oliver, R. Fernandez. Predicting Alzheimer’s
Disease Using Driving Simulator Data. \textit{In 2020 42nd Annual International Conference of
the IEEE Engineering in Medicine and Biology Society}, 2020, pp. 5432-5435. IEEE.

\sectionsep

\end{minipage}



\end{document}  \documentclass[]{article}
